DeepSphere: a graph-based spherical CNN

### 2020-02-14 main.tex
small edits

\subsection{Problem formulation}
% 0.1 Explain the sampling problem
%As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
A continuous function $f : \mathcal C(\S^2) \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: C(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$. We require $F_\V$ to be a suitable subspace of continuous functions such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most samplings, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling where a sampling theorem holds, and thus a closed-form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
For samplings where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

% 0.2 Explain why the Laplacian is so important...
By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $\Rg, g\in SO(3)$: $\Rg f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
Hence, if $\Rg$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, $h(\b{L})$ is rotation equivariant if and only if
% 0.3 Formulate the problem
\begin{equation*} %\label{eq:equivariance}
	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f}, \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
\end{equation*}
where $\b{R}_\V(g) = T_\V \Rg T_\V^{-1}$.
For an empirical evaluation of equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$ and a  rotation $g$ as
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2.
\end{equation}
More generally for a class of signals $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g)
\end{equation}
represents the overall equivariance error.
The expected value is obtained by averaging over a finite number of random functions and random rotations.

>>>>

\subsection{Problem formulation}
% 0.1 Explain the sampling problem
%As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
A continuous function $f : \mathcal C(\S^2) \supset F_\V \to \R$ is sampled as $T_\V(f) = \b{f}$ by the sampling operator $T_\V: C(\S^2) \supset F_\V \to \R^n$ defined as $\b{f}: f_i=f(x_i)$.
We require $F_\V$ to be a suitable subspace of continuous functions such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling $\V$ and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most samplings, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling where a sampling theorem holds, and thus a closed-form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
For samplings where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

% 0.2 Explain why the Laplacian is so important...
By definition, the (spherical) graph convolution is rotation equivariant if and only if it commutes with the rotation operator defined as $\Rg, g\in SO(3)$: $\Rg f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian \eqnref{graph_conv}.
Hence, if $\Rg$ commutes with $\b{L}$, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, $h(\b{L})$ is rotation equivariant if and only if
% 0.3 Formulate the problem
\begin{equation*} %\label{eq:equivariance}
	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f}, \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
\end{equation*}
where $\b{R}_\V(g) = T_\V \Rg T_\V^{-1}$.
For an empirical evaluation of equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$ and a  rotation $g$ as
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2.
\end{equation}
More generally for a class of signals $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g)
\end{equation}
represents the overall equivariance error.
The expected value is obtained by averaging over a finite number of random functions and random rotations.
